Pillar 1 - Sequential Pattern Mining

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
typo

  # itemID
  mutate(
    item    = `Course ID`,
    item_PF = if_else(Grade >= pass_grade, paste_(item, "pass"), paste_(item, "fail")),
    item_PF = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
    )
```

>>>>

  # itemID
  mutate(
    item    = `Course ID`,
    item_PF = if_else(Grade >= pass_grade, paste_(item, "pass"), paste_(item, "fail")),
    item_HL = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
    )
```
